Direction-Selective Resistance to Cerebrospinal-Fluid Flow As the Generative Mechanism of Syringomyelia

### 2022-07-23 manuscript/main.tex
Revision of manuscript/main.tex

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{newfloat}
\DeclareFloatingEnvironment{video}
\title{Direction-Selective Resistance to Cerebrospinal-Fluid Flow As
the Mechanism of Syrinx Generation in Syringomyelia}

@@

\keywords{syringomyelia, pathophysiology, simulation}
\input{embed_video.tex}
\begin{abstract}
    The pathophysiology of syringomyelia is not well understood. The main
    theoretical problem is how cerebrospinal fluid (CSF) enters from
    low-pressure subarachnoid space to high-pressure syrinx and remains
    inside the syrinx. We approached this problem with computer simulation
    of the CSF flow in the spine.
\end{abstract}
\begin{document}

@@

The pathophysiology of syringomyelia is still poorly understood. A number
of hypotheses exist in the literature \cite{gardner1958mechanism,
williams1980pathogenesis, milhorat1999chiari, ball1972pathogenesis,
klekamp2002pathophysiology, duboulay1974mechanism, heiss1999elucidating,
milhorat1993anatomical, stoodley2000pathophysiology, terae1994increased,
chang2003hypothesis, chang2004theoretical, greitz2006unraveling}, but they
provide widely different explanations on the mechanisms of syrinx
generation.  Nevertheless, most researchers seem to agree on the following
points. First, the syrinx fluid is identical to the CSF, and there should
be some communication between the syrinx and the subarachnoid space. This
point is supported by many studies \cite{ellertsson1969syringomyelia,
ellertsson1969myelocystographic, li1987conventional, heiss2019origin},
although a few different opinions exist \cite{greitz2006unraveling,
koyanagi1997surgical}. Second, some derangement of CSF flow in the spinal
subarachnoid space causes syrinx both in Chiari-I malformation
\cite{wolpert1994chiari, bhadelia1995cerebrospinal, heiss1999elucidating,
hofmann2000phasecontrast, quigley2004cerebrospinal} and subarachnoid
arachnopathy \cite{klekamp1997treatment, brodbelt2003altered,
heiss2012pathophysiology, chang2014dorsal}. Notably, the cerebellar tonsil
deranges the CSF flow in the former and adhesive arachnoiditis in the
latter.

The problem, however, is where this communicating channel resides and what
mechanism generates the syrinx. On these points, there is no solid
experimental or clinical evidence, and the opinions of researchers deviate
widely. Gardner et al. \cite{gardner1958mechanism} thought that the central
canal intercommunicates the syrinx and the fourth ventricle, and arterial
pressure waves exerted on the central canal generate the syrinx. Williams
et al. also postulated the communication through the central canal, but for
the syrinx generation mechanism, he emphasized the craniospinal pressure
gradient produced by Valsalva maneuver et al
\cite{williams1980pathogenesis}.

On the other hand, Ball and Dayan \cite{ball1972pathogenesis} assumed that
CSF enters the syrinx through the perivascular space of arteries
penetrating the spinal cord. This idea has the following variations. Heiss
et al.  \cite{heiss1999elucidating} proposed that the piston-like movement
of the cerebellar tonsils in Chiari-I patients generates pressure waves in
the spinal subarachnoid space, which subsequently drive CSF into the syrinx
through the perivascular space. Stoodley et al. also considered the
perivascular space as the communicating channel, but he assumed the
arterial pulse pressure as the driving force of CSF
\cite{stoodley2000mechanisms} All these assumptions are not proven and
remain hypothetical. Although the perivascular-space theory seems to be
favored by recent researchers, there remains the possibility that a thin
communicating channel exists between the syrinx and the fourth ventricle
\cite{chang2021hypothesis}.

@@

As to the first point, there are different syringomyelia types, such as
Chiari-I-malformation and spinal-arachnopathy-related
\cite{klekamp1997treatment}. The Chiari-I-malformation-related
syringomyelia is further divided into communicating and non-communicating
\cite{elliott2013syringomyelia}. For each of them, current theories assume
a distinct mechanism of syrinx generation. However, it may be more natural
to conjecture some common mechanism underlying these different types of
syringomyelia \cite{stoodley2000mechanisms}.  The second point is
theoretically essential but challenging to solve. Physical theories dictate
that the expanded syrinx cavity has higher pressure than the subarachnoid
space \cite{serwayr.a.2016fluids, heiss1999elucidating,
davis1989mechanisms, ellertsson1970distending}. Therefore, merely assuming
a communicating channel does not explain how CSF enters the syrinx and
remains inside against this pressure gradient. Even if we take a specific
time window where the subarachnoid pressure exceeds the syrinx pressure, it
does not explain how the CSF remains inside the syrinx after it.

The current article is part of our effort to solve the above theoretical
problems. In our previous paper \cite{chang2021hypothesis}, we hypothesized
that if there is a resistance to CSF flow in a particular direction
(rostral or caudal), it causes a one-way valve-like effect on a CSF channel
inside the spinal cord, leading to the accumulation of CSF and generation
of a syrinx. This hypothesis was attractive to us because it could explain
the pathophysiology of both Chiari-I-malformation-related syringomyelia and
arachnopathy-related syringomyelia. Namely, in
Chiari-I-malformation-related syringomyelia, the herniated cerebellar
tonsils may function as a direction-selective resistance. In
arachnopathy-related syringomyelia, some arachnoid adhesion may play the
same function \cite{chang2014dorsal}.  However, in that article, we just
drew a rough sketch of this process and left out a detailed explanation.
The current article will describe in detail how direction-selective
resistance in the subarachnoid space generates a one-way valve mechanism in
the CSF channel inside the spinal cord.

For this purpose, we used a mathematical model simulating the CSF movement
of the spine---a revised version of our previous model \cite{chang2003hypothesis,
chang2004theoretical}. This model describes the spinal CSF movement as an
electric current in a modeled circuit (a lumped parameter model with
multiple compartments \cite{shi2011review}), and it assumes the existence of a
patent central canal. We placed a direction-selective resistance in this
model at a certain point in the spinal subarachnoid space and observed how
it affects the CSF flow in the central canal.

@@

Some problem exists in the computer simulation of the motion of biological
fluids such as blood and CSF. Such bodily fluids move inside flexible
tubes. It, therefore, requires different analysis techniques from those
used in the engineering field, where the boundary of the conduit is
supposed to be solid. For this purpose, researchers widely used lumped
parameter models \cite{shi2011review, kokalari2013review}. This model
considers the fluid flow inside a flexible tube in analogy to the flow of
electricity in an electric circuit. The accumulation of electricity in a
capacitor represents the expansion of a flexible tube and the accompanying
pressure elevation. An electrical resistor represents the frictional
resistance to flow. This model has a wide variety. For example, it may
model the whole cardiovascular system as one electric circuit, or it may
model it as a synthesis of multiple compartments of electric circuits
\cite{shi2011review, kokalari2013review}. Our current model is the type of a
lumped parameter model with multiple compartments.  In this study, we did
not intend to make a quantitatively precise model of the spinal CSF flow
but to make a basic model that reveals the phenomenon underlying the
generation of syringomyelia. For this purpose, we adopted a revised version
of our previous lumped parameter model with multiple compartments.

Previously, we developed a mathematical model that simulated the CSF flow
in the spine \cite{chang2003hypothesis, chang2004theoretical}. This model (a
multiple-compartment version of a 1-dimensional lumped parameter model)
could describe the CSF movement in the whole spine (Figure \ref{fig:model}).

@@

A set of differential equations can describe the behavior of this model.
Using computer software, we can numerically calculate its behavior to a
cranial pressure wave (defined as a boundary condition on the cranial
points).  This time, we improved the previous model as follows.

\begin{itemize}
    \item We increased the number of compartments from 10 to 100,
        thereby making the model more precise.
    \item We estimated the values of the parameters
        (the capacitance and resistance of each component)
        of the model as follows so that the model will become more realistic.
        \begin{itemize}
            \item First, we set the length of the modeled spinal cord to be 1 meter.
            \item The resistance of the subarachnoid space ($R$) was
                estimated using the following equations of Poisseuille
                \cite{brook1999numerical, sherwin2003computational, huilgol2020fast}. 
             $$\Delta P=\frac{8\pi \mu{}LQ}{A^{2}}=RQ$$
                \begin{itemize}
                    \item $\Delta P$: Pressure difference between the adjacent compartments
                    \item Q: flow speed per unit surface
                    \item $\mu$: viscosity coefficient. In this case, it was set to the value of water (0.0007).
                    \item L: distance between the adjacent compartments. It was set to 1 cm.
                    \item A: cross sectional area of the subarachnoid
                        space. It was set to the value of a concentric
                        annulus \cite{huilgol2020fast} with the outer diameter of 1cm and the inner diameter of 0.7 cm ($1.6\times{}10^{-4} (m^2)$) 
                \end{itemize}
            \item Thus, $R$ was calculated to be $6872\hspace{0.2cm}(Pa\cdot{}sec/m^3)$
            \item The resistance of the central canal ($r$) was estimated
                using the same equation with $A$ set to
                $\pi{}(10^{-4})^2\hspace{0.1cm}(m^2)$, i.e. the cross
                sectional area of a tube with a diameter of 100 $\mu{}m$.
                Thus, $r$ was calculated to be $1.78\times10^{11}\hspace{0.2cm}(Pa\cdot{}sec/m^3)$
        \end{itemize}
    \item We determined the capacitance ($C_{sub}$)corresponding to the dural elasticity so that the pressure-wave velocity determined by the time constant ($RC$) will roughly correspond to the pressure-wave velocity of the downward CSF wave observed in phase-contrast MRI of normal individuals. Thus, we set $C_{sub}=0.1\hspace{0.2cm}(m^3/Pa\cdot{}sec)$.
\end{itemize}

Figure 1 shows the scheme of the constructed electric circuit model. This
model represents the CSF movement in the spine as electric flow through
multiple compartments of capacitances connected with resistors. Table 1
shows the values of the resistors and capacitors of the system.  A set of
differential equations can describe the behavior of this electric circuit,
and we can solve it numerically by setting the voltage at the cranial nodes
as the boundary condition (Figure \ref{fig:circuit}). In the previous articles
\cite{chang2003hypothesis, chang2004theoretical}, we only analyzed the
transient behavior of the model to a sudden pressure increase on the
cranial side of the subarachnoid space. This analysis helped simulate the
situation of coughing or Valsalva maneuvers. In this article, however, we
analyzed the steady-state response of the model to an oscillating cranial
pressure wave simulating the normal cardiac pulsation of the CSF.

@@

We numerically solved the differential equations using computer software
(Mathematica version 12, Wolfram Research, Champaign, IL, U.S.A.). We set
the boundary conditions as follows. (1) The voltage at the two cranial
nodes was set to a sine wave oscillating around 100 mmHg with an amplitude
of 20 mmHg at one cycle per second. (2) The initial dural pressure was set
at 100 mmHg in all segments. We set the step of the numerical solution to
1/5000 second and calculated the solution from zero to 20 seconds. We
displayed the obtained solution as a movie in mp4 format.

@@

We present the systems' responses to twenty cycles of to-and-fro waves as
animations. The x-axis of each animation represents the 100 nodes of the
circuit laid out from the cranial to caudal direction. The y-axis displays
some of the following four measures: the dural tension (voltage in D
capacitors in Figure 2), the canal tension (voltages in C capacitors), the
subarachnoid CSF flow (flows in R resistors), and the canal flow (flows in
r resistors). We plotted the caudal flow in the positive and the rostral
flow in the negative direction. The pressure values are shown in $cmH_2O$,
the flows in $ml/sec$. To plot the four measures in a single animation, we
multiplied the following three measures---the canal tension, the
subarachnoid CSF flow, and the canal flow---with the following
coefficients, respectively: namely, the canal tension with 50, the
subarachnoid flow with 0.005, and the canal flow with $1.5\times10^{5}$.

Video \ref{video:norm} shows the original system's response representing
the normal condition. In this state, CSF makes a smooth to-and-fro movement
in the subarachnoid space with the corresponding pressure wave along the
dura and the central canal. CSF also makes to-and-fro movements in the
canal.

\begin{video}[hbt]
    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_norm.jpg}}{totalAnimationNorm.mp4}
    \caption{Video showing the normal circuit response}
    \label{video:norm}
\end{video}

In Video \ref{video:simple_block}, we increased the subarachnoid resistance
$R_{25}$ by 20 times, thereby simulating a simple block of the subarachnoid
flow in both directions. In this condition, both the caudal and rostral
flow along the resistance produced a drop of the dural tension downstream
to the resistance, corresponding to the increased resistance both in the
caudal and rostral flow phases. This pressure drop caused an increase in
canal flow in the same direction as the subarachnoid flow. This increased
canal flow caused a transient increase in the canal pressure distal to the
block and a decrease proximal to the block. However, these pressure changes
alternated along the alternation of the flow direction and did not produce
a sustained pressure increase.

\begin{video}[hbt]
    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_simple_block.jpg}}{totalAnimationSb.mp4}
    \caption{Video showing the response of the circuit with a simple
    resistor at point 25}
    \label{video:simple_block}
\end{video}

\begin{video}[hbt]
    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{totalAnimation.mp4}
    \caption{Video showing the response of the circuit with a
    direction-selective resistor at point 25}
    \label{video:oneway}
\end{video}

\begin{video}[hbt]
    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{canalFlowOneway.mp4}
    \caption{Video showing the canal flow in the model with
    direction-selective resistance at point 25}
    \label{video:canal_flow_oneway}
\end{video}

\begin{video}[hbt]
    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{canalFlowComparison.mp4}
    \caption{Video showing the canal flow in the two models: simple
    resistance at point 25 and direction-selective resistance at point 25}
    \label{video:canal_comparison}
\end{video}

@@

In this article, we theoretically analyzed the CSF movement in the spinal
cord using a lumped parameter model with multiple components. It simulated
a system with an elastic tube (dura) containing an elastic cylindrical
material (spinal cord) that itself had a fluid channel inside (the central
canal). When we placed a direction-selective resistor in the subarachnoid
space and evoked a to-and-fro pressure wave on this system, it produced a
sustained pressure elevation in the segment distal to the
direction-selective resistor. This phenomenon may explain the pathogenesis
of syringomyelia both in Chiari I malformation and syringomyelia associated
with arachnopathy.

Subarachnoid pressure affects the pressure inside the central canal. As
seen in Figure \ref{fig:circuit}, the absolute pressure inside the central
canal is the sum of the subarachnoid and canal pressure (voltages of $C_k$
and $D_k$ in electrical terms). Suppose a one-way valve selectively resists
caudal flow in the subarachnoid space at point A. Caudal CSF flow creates a
pressure drop across this valve, with the distal pressure smaller than the
proximal one. It decreases the absolute canal pressure distal to point A
because it is the sum of the subarachnoid pressure and the canal pressure.
It, therefore, creates a pressure gradient in the central canal across
point A, thereby increasing the distal CSF flow in the canal at that point
(Figure \ref{fig:pump_close}).

@@

On the contrary, reverse flow, not encountering resistance, does not create
a pressure drop (Figure \ref{fig:pump_open}). Although some of the CSF that
had been pumped caudally during the caudal-flow phase will flow back
rostrally, its amount will be smaller. The net result will be that some CSF
is pumped caudally in one cycle of the to-and-fro movement. Thus, CSF
gradually accumulates in the distal segment of the resistance (Video 3). We
hypothesize that this is the mechanism underlying the syrinx generation.

@@

This hypothesis solves the theoretical problems pointed out in the
Introduction. A one-way valve in subarachnoid space creates an asymmetry of
the pressure gradient between the caudal and rostral flow phases in the
central canal. This asymmetric alternation of pressure gradient effectively
pumps CSF caudally, creating sustained pressure elevation in the caudal
segment. In other words, the energy of the to-and-fro CSF movement is
translated via the one-way valve into the creation and sustenance of
syringomyelia.

@@

Also, there is a possibility that some types of arachnoid pathology
function as one-way valves. In 2014, we reported a case of thoracic
arachnoid web associated with syringomyelia, in which phase-contrast MRI
detected one-way-valve-like behavior of the arachnoid web
\cite{chang2014dorsal}. We found an obliquely oriented arachnoid web that
reminded us of a one-way valve in surgery. Thus, our hypothesis may also
solve the second theoretical problem that we pointed out in the
Introduction. Namely, we may consider the presence of a one-way valve in
spinal subarachnoid space as a common mechanism underlying both
Chiari-I-related and arachnopathy-related syringomyelia.  Our theory
assumes that the arterial-pulse generated to-and-fro CSF movement provides
the energy for syrinx generation. It is compatible with Stoodley et al.'s
experimental result that syrinx maintenance is dependent on arterial
pulsation \cite{stoodley2000mechanisms}. In this study, the authors showed that

>>>>

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{newfloat}
\DeclareFloatingEnvironment{video}
\title{Direction-Selective Resistance to Cerebrospinal-Fluid Flow As
the Generative Mechanism of Syringomyelia}

@@

\keywords{syringomyelia, pathophysiology, simulation}
\input{embed_video.tex}
\begin{abstract}

    The pathophysiology of syringomyelia is not well understood. The main
    theoretical problem unaddressed by previous hypotheses is how
    cerebrospinal fluid (CSF) enters from low-pressure subarachnoid space
    to high-pressure syrinx and remains inside. We approached this problem
    with a computer simulation of the CSF flow in the spine. We
    hypothesized that to-and-fro movement of CSF across a
    direction-selective resistance, via the pressure drop caused by the
    resistance, pumps the CSF in the intraspinal channel distally.

    We constructed a model of CSF dynamics in the spine, which was an
    electric circuit based on a lumped parameter model with multiple
    compartments. The model assumed a CSF channel inside the spinal cord.
    With this model, we could analyze the to-and-fro CSF movement of the
    spine. We then created a direction-selective resistance in the
    subarachnoid space. We changed a subarachnoid resistor so that it would
    resist only to the caudally-directed flow.

    In the caudal flow phase, flow across the replaced resistor produced a
    pressure drop in the distal subarachnoid segment. It subsequently
    decreased the spinal-channel pressure in the distal segment; thus, the
    pressure gradient across the point increased. This increased pressure
    gradient pumped the CSF in the channel caudally. Because this
    phenomenon did not occur in the rostral flow phase, the rostral flow in
    the channel during this phase was smaller.  Overall, each cycle of
    to-and-fro CSF movement pumped some CSF caudally in the spinal channel.

    We could reasonably hypothesize that to-and-fro CSF movement across a
    direction-selective resistance was the generative mechanism of
    syringomyelia.

\end{abstract}
\begin{document}

@@

The pathophysiology of syringomyelia is still poorly understood. Many
hypotheses exist in the literature \cite{gardner1958mechanism,
williams1980pathogenesis, milhorat1999chiari, ball1972pathogenesis,
klekamp2002pathophysiology, duboulay1974mechanism, heiss1999elucidating,
milhorat1993anatomical, stoodley2000pathophysiology, terae1994increased,
chang2003hypothesis, chang2004theoretical, greitz2006unraveling}, but they
provide widely different explanations on the mechanisms of syrinx
generation. We may, however, enumerate what few consensuses as follows.
First, the syrinx fluid is identical to the CSF, and there is some
communication between the syrinx and the subarachnoid space. Many studies
support this point \cite{ellertsson1969syringomyelia,
ellertsson1969myelocystographic, li1987conventional, heiss2019origin},
albeit some different opinions \cite{greitz2006unraveling,
koyanagi1997surgical}. Second, some derangement of CSF flow in the spinal
subarachnoid space causes syrinx both in Chiari-I malformation
\cite{wolpert1994chiari, bhadelia1995cerebrospinal, heiss1999elucidating,
hofmann2000phasecontrast, quigley2004cerebrospinal} and subarachnoid
arachnopathy \cite{klekamp1997treatment, brodbelt2003altered,
heiss2012pathophysiology, chang2014dorsal}. Notably, the cerebellar tonsil
deranges the CSF flow in the former and adhesive arachnoiditis in the
latter.

The problem, however, is where this communicating channel resides and what
mechanism generates the syrinx. On these points, there is no solid
experimental or clinical evidence, and the opinions of researchers vary
widely. Gardner et al. \cite{gardner1958mechanism} thought that the central
canal intercommunicates the syrinx and the fourth ventricle. Arterial
pulses then exert pressure waves on the central canal and generate the
syrinx. Williams et al. also postulated the communication through the
central canal. He, however, emphasized the craniospinal pressure gradient
produced by Valsalva maneuver et al. \cite{williams1980pathogenesis}.

On the other hand, Ball and Dayan \cite{ball1972pathogenesis} assumed that
CSF entered the syrinx through the perivascular space of arteries
penetrating the spinal cord. This idea has the following variations. Heiss
et al.  \cite{heiss1999elucidating} proposed that the piston-like movement
of the cerebellar tonsils in Chiari-I patients generated pressure waves in
the spinal subarachnoid space. And it subsequently drove CSF into the
syrinx through the perivascular space. Stoodley et al. also considered the
perivascular space as the communicating channel, but he assumed the
arterial pulse pressure as the driving force \cite{stoodley2000mechanisms}.
All these assumptions are not proven and remain hypothetical. Although
recent researchers seem to favor the perivascular-space theory, there
remains the possibility that a thin communicating channel exists between
the syrinx and the fourth ventricle \cite{chang2021hypothesis}.

@@

As to the first point, there are different syringomyelia types, such as
Chiari-I-malformation and spinal-arachnopathy-related
\cite{klekamp1997treatment}. The Chiari-I-malformation-related
syringomyelia is further divided into communicating and non-communicating
\cite{elliott2013syringomyelia}. Current theories cannot explain these
different types of syringomyelia in a unified fashion. However, it may be
more natural to conjecture some common mechanism underlying these different
types of syringomyelia \cite{stoodley2000mechanisms}. The second point is
theoretically essential but challenging. Physical laws dictate that the
expanded syrinx cavity has higher pressure than the subarachnoid space
\cite{serwayr.a.2016fluids, heiss1999elucidating, davis1989mechanisms,
ellertsson1970distending}, which is understandable considering the elastic
tension of the syrinx wall that the inside pressure confront. Therefore,
merely assuming a communicating channel does not explain how CSF enters the
syrinx against this pressure gradient and remains inside. Even if we take a
specific time window where the subarachnoid pressure exceeds the syrinx
pressure, it does not explain how the CSF remains inside the syrinx after
it.

The current article is part of our effort to solve the above theoretical
problems. We proposed in our previous paper \cite{chang2021hypothesis} a
hypothesis on the pathophysiology of syringomyelia. We hypothesized that a
direction-selective resistance to spinal subarachnoid CSF flow causes
syringomyelia. Suppose there is a resistance to spinal CSF flow only in
the, e.g., caudal direction. To-and-fro CSF movement across it will pump
CSF in an intraspinal channel caudally, causing syringomyelia. This
hypothesis could solve the two problems discussed above. It could solve the
paradox of CSF movement against the pressure gradient. Also, it could
explain the pathophysiology of both Chiari-I-malformation-related
syringomyelia and arachnopathy-related syringomyelia. The herniated
cerebellar tonsils function as the selective resistance in Chiari-I
malformation. And some arachnoid valve plays that role in
arachnopathy-related syringomyelia \cite{chang2014dorsal}. However, in that
article, we just drew a rough sketch of this process and left out a
detailed explanation. The current article will describe this mechanism in
detail using computer simulation.

For this purpose, we used a mathematical model simulating the CSF movement
of the spine. We revised a lumped parameter model with multiple
compartments used in our previous articles \cite{chang2003hypothesis,
chang2004theoretical}.  We placed a direction-selective resistance in this
model at a certain point in the spinal subarachnoid space. We then observed
how it affected the CSF flow in the channel inside the spinal cord.

@@

Some problem exists in the computer simulation of the motion of biological
fluids such as blood and CSF. Such bodily fluids move inside flexible
tubes. It differs from the usual situation of fluid mechanics, where the
boundary of the fluid conduit is solid. Thus, we cannot simply apply the
standard Navier-Stokes equations for our simulation. For this reason,
researchers have commonly used lumped parameter models \cite{shi2011review,
kokalari2013review}. This model considers the fluid flow inside a flexible
tube analogous to the electric flow in an electric circuit. The
accumulation of electricity in a capacitor represents the expansion of a
flexible tube and the accompanying pressure elevation. An electrical
resistor represents the frictional resistance to flow. This model has a
wide variety. For example, it may model the whole cardiovascular system as
one electric circuit, or it may model it as a synthesis of multiple
compartments of electric circuits \cite{shi2011review, kokalari2013review}.
Our current model is the type of lumped parameter model with multiple
compartments that simulates the CSF dynamics in the spine and is an updated
version of the model used in our previous articles
\cite{chang2003hypothesis, chang2004theoretical}. In this study, we did not
intend to make a quantitatively precise model of the spinal CSF flow but to
make a basic model that reveals the phenomenon underlying the generation of
syringomyelia.

Previously, we developed a mathematical model that simulated the CSF flow
in the spine \cite{chang2003hypothesis, chang2004theoretical}. This model (a
multiple-compartment version of a 1-dimensional lumped parameter model)
could describe the CSF movement in the whole spine (Figure
\ref{fig:model}). In this model, the \textit{D} capacitors represented the
dural tension, \textit{C} capacitors the tension of the central canal,
\textit{R} resistors the frictional resistance in the subarachnoid space,
and \textit{r} resistors the frictional resistance in the central canal.

@@

Figure \ref{fig:circuit} shows the bare electric circuit extracted from
Figure \ref{fig:model}. A set of differential equations could describe the
behavior of this model.  Using computer software, we could numerically
calculate its behavior in response to a certain cranial pressure wave
(defined as a boundary condition on the cranial nodes). This time, we
improved the previous model as follows.

\begin{itemize}
    \item We increased the number of compartments from 10 to 100,
        thereby making the model more precise.
    \item We revised the values of the parameters
        (the capacitance and resistance of each component)
        of the model as follows so that the model will become more realistic.
        \begin{itemize}
            \item First, we set the length of the modeled spinal cord to be 1 meter.
            \item The resistance of the subarachnoid space ($R$) was
                estimated using the following equations of Poisseuille
                \cite{brook1999numerical, sherwin2003computational, huilgol2020fast}. 
             $$\Delta P=\frac{8\pi \mu{}LQ}{A^{2}}=RQ$$
                \begin{itemize}
                    \item $\Delta P$: Pressure difference between the adjacent compartments
                    \item Q: flow speed per unit surface
                    \item $\mu$: viscosity coefficient. In this case, it was set to the value of water (0.0007).
                    \item L: distance between the adjacent compartments. It was set to 1 cm.
                    \item A: cross sectional area of the subarachnoid
                        space. It was set to the value of a concentric
                        annulus \cite{huilgol2020fast} with the outer diameter of 1cm and the inner diameter of 0.7 cm ($1.6\times{}10^{-4} (m^2)$) 
                \end{itemize}
            \item Thus, $R$ was calculated to be $6872\hspace{0.2cm}(Pa\cdot{}sec/m^3)$
            \item The resistance of the central canal ($r$) was estimated
                using the same equation with $A$ set to
                $\pi{}(10^{-4})^2\hspace{0.1cm}(m^2)$, i.e. the cross
                sectional area of a tube with a diameter of 100 $\mu{}m$.
                Thus, $r$ was calculated to be $1.78\times10^{11}\hspace{0.2cm}(Pa\cdot{}sec/m^3)$
        \end{itemize}
    \item We determined the capacitance ($C_{sub}$)corresponding to the dural elasticity so that the pressure-wave velocity determined by the time constant ($RC$) will roughly correspond to the pressure-wave velocity of the downward CSF wave observed in phase-contrast MRI of normal individuals. Thus, we set $C_{sub}=0.1\hspace{0.2cm}(m^3/Pa\cdot{}sec)$.
\end{itemize}

Figure \ref{fig:model} shows the scheme of the constructed electric circuit
model. This model represents the CSF movement in the spine as electric flow
through multiple compartments of capacitances connected with resistors.
Table 1 shows the values of the resistors and capacitors of the system. A
set of differential equations can describe the behavior of this electric
circuit, and we can solve it numerically by setting the voltage at the
cranial nodes as the boundary condition (Figure \ref{fig:circuit}). In the
previous articles \cite{chang2003hypothesis, chang2004theoretical}, we only
analyzed the transient behavior of the model to a sudden pressure increase
on the cranial side of the subarachnoid space. This analysis helped
simulate the situation of coughing or Valsalva maneuvers. In this article,
however, we analyzed the response of the model to an oscillating cranial
pressure wave simulating the normal cardiac pulsation of the CSF.

@@

We numerically solved the differential equations using computer software
(Mathematica version 12, Wolfram Research, Champaign, IL, U.S.A.) on a
personal computer. We set the boundary conditions as follows. (1) The
voltage at the two cranial nodes was set to a sine wave oscillating around
10 $cmH_{2}O$ with an amplitude of 20 $cmH_{2}O$ at one cycle per second.
(2) The initial dural pressure was set at 10 $cmH_{2}O$ in all segments. We
set the step of the numerical solution to 1/5000 second and calculated the
solution from zero to 20 seconds. We displayed the obtained solution as a
movie in mp4 format.

@@

We present the systems' responses in animations showing twenty cycles of
to-and-fro waves. The x-axis of each animation represents the 100 nodes of
the circuit laid out from the cranial to caudal direction. The y-axis
displays some of the following four measures: the dural tension (voltage in
D capacitors in Figure 2), the canal tension (voltages in C capacitors),
the subarachnoid CSF flow (flows in R resistors), and the channel flow
(flows in r resistors). We plotted the caudal flow in the positive and the
rostral flow in the negative direction. The pressure values are shown in
$cmH_2O$, the flows in $ml/sec$. To plot the four measures in a single
animation, we multiplied the following three measures---the canal tension,
the subarachnoid CSF flow, and the canal flow---with the following
coefficients, respectively: namely, the canal tension with 50, the
subarachnoid flow with 0.005, and the canal flow with $1.5\times10^{5}$.

Video \ref{video:norm} shows the original system's response representing
the normal condition. In this state, CSF made a smooth to-and-fro movement
in the subarachnoid space with the corresponding pressure wave along the
dura and the central canal. CSF also made smooth to-and-fro movements in
the channel.

%\begin{video}[hbt]
%    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_norm.jpg}}{totalAnimationNorm.mp4}
%    \caption{Video showing the normal circuit response}
%    \label{video:norm}
%\end{video}

In Video \ref{video:simple_block}, we increased the subarachnoid resistance
$R_{25}$ by 20 times, thereby simulating a simple block of the subarachnoid
flow in both directions. In this condition, both the caudal and rostral
flow across the resistance produced pressure drop in the distal
subarachnoid segment.  This pressure drop caused an increase in canal flow
in the same direction as the subarachnoid flow. This increased canal flow
caused a transient increase in the canal pressure distal to the block and a
decrease proximal to the block. However, these pressure changes alternated
along the alternation of the flow direction and did not produce a sustained
pressure increase.

%\begin{video}[hbt]
%    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_simple_block.jpg}}{totalAnimationSb.mp4}
%    \caption{Video showing the response of the circuit with a simple
%    resistor at point 25}
%    \label{video:simple_block}
%\end{video}
%
%\begin{video}[hbt]
%    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{totalAnimation.mp4}
%    \caption{Video showing the response of the circuit with a
%    direction-selective resistor at point 25}
%    \label{video:oneway}
%\end{video}

%\begin{video}[hbt]
%    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{canalFlowOneway.mp4}
%    \caption{Video showing the canal flow in the model with
%    direction-selective resistance at point 25}
%    \label{video:canal_flow_oneway}
%\end{video}
%
%\begin{video}[hbt]
%    \embedvideo*{\includegraphics[width=\textwidth]{thumbnail_oneway.jpg}}{canalFlowComparison.mp4}
%    \caption{Video showing the canal flow in the two models: simple
%    resistance at point 25 and direction-selective resistance at point 25}
%    \label{video:canal_comparison}
%\end{video}

@@

In this article, we theoretically analyzed the CSF movement in the spine
using a lumped parameter model with multiple components. It simulated a
system with an elastic tube (dura) containing an elastic cylindrical
material (spinal cord) that itself had a fluid channel inside (e.g. the
central canal). When we placed a direction-selective resistor in the
subarachnoid space and evoked a to-and-fro pressure wave on this system, it
produced a sustained pressure elevation in the segment distal to the
resistor in the resisted direction. This phenomenon may explain the
pathogenesis of syringomyelia both in Chiari I malformation and
syringomyelia associated with arachnopathy.

Subarachnoid pressure pushes the spinal cord material and affects the
pressure inside the central canal. As seen in Figure \ref{fig:circuit}, the
absolute pressure inside the central canal is the sum of the subarachnoid
and canal tension (voltages of $C_k$ and $D_k$ in electrical terms).
Suppose a one-way valve selectively resists caudal flow in the subarachnoid
space at point $A$. Caudal CSF flow creates a pressure drop across point
$A$, with the caudal pressure smaller than the proximal one. Thus, the
absolute pressure in the canal distal to point $A$ become smaller because
the outside subarachnoid pressure there is smaller. It, therefore, creates
a pressure gradient in the central canal across point $A$, thereby
increasing the distal CSF flow in the canal at that point (Figure
\ref{fig:pump_close}).

@@

On the contrary, rostral flow, not encountering resistance, does not create
a pressure drop (Figure \ref{fig:pump_open}). Although some of the CSF that
had been pumped caudally during the caudal-flow phase will flow back
rostrally, its amount will be smaller. The net result will be that some CSF
is pumped caudally in one cycle of the to-and-fro movement. Thus, CSF
gradually accumulates in the distal segment of the resistance (Video 3). We
hypothesize that this is the mechanism underlying the syrinx generation.

@@

This theory successfully explains how CSF is pumped against the pressure
gradient and remains inside the syrinx, one of the problems pointed out in
the Introduction. A one-way valve in subarachnoid space creates an
asymmetry of the pressure gradient between the caudal and rostral flow
phases in the central canal. This asymmetric alternation of pressure
gradient effectively pumps CSF caudally, creating sustained pressure
elevation in the caudal segment. In other words, the energy of the
to-and-fro CSF movement is translated via the one-way valve into the
creation and sustenance of syringomyelia.

@@

Also, there is a possibility that some types of arachnoid pathology
function as one-way valves. In 2014, we reported cases of thoracic
arachnoid web associated with syringomyelia, in which phase-contrast MRI
detected one-way-valve-like behavior of the arachnoid web
\cite{chang2014dorsal}. In surgery, we found an obliquely oriented
arachnoid web that reminded us of a one-way valve. Thus, our hypothesis may
also solve the second theoretical problem we pointed out in the
Introduction. Namely, we may consider the presence of a one-way valve in
spinal subarachnoid space as a common mechanism underlying both
Chiari-I-related and arachnopathy-related syringomyelia.

Our theory clearly explained how the energy of the to-and-fro CSF movement
was transformed to CSF movement into the syrinx. However, previous
theories seemed to have difficulty in explaining this process. According to
the theories of Heiss et al. \cite{heiss1999elucidating} or that of
Stoodley et al. \cite{stoodley2000mechanisms}, the energy is provided by
either enhanced pressure waves in subarachnoid space or pulsation of spinal
arteries. However, none of these theories explains the detailed mechanism

hypothesized that arterial pulses drive CSF
into the perivascular space of the cord matrix. Although his hypothesis
explains the energy for syrinx generation, it fails to explain why
manipulation of Our theory reasonably
explained how the motion energy of the flowing CSF pumps CSF in the channel
inside the spinal cord. It is compatible with Stoodley et al.'s
experimental result that syrinx maintenance is dependent on arterial
pulsation . In this study, the authors showed that
